Data-based completion of grey-box models with neural networks

### 2020-10-23 systemID_NNs.tex
make some writing edits in a little bit.
getting closer.

In this example, the network just approximates a linear function.
The figure below shows validation performances of the grey-box 
and augmented hybrid models. The structure 
of the network is restricted to just a matrix and
the augmented model was trained on 120 samples.

\begin{figure}[!h]
  \centering
  \includegraphics[page=2, width=\textwidth]{tworeac_plots_lin.pdf}
\end{figure}

@@

The grey-box model is kept the same. The parameters 
in the model are modified to 
$k_1 = 1 \ \textnormal{m}^3/\textnormal{min}, 
\ k_2 = 0.05 \ \textnormal{m}^3/\textnormal{min},
\ k_3 = 0.1 \ \textnormal{m}^3/\textnormal{min}$, 
and $\tau = 5 \ \textnormal{min}$.
An augmented model with a neural
network architecture [8, 4, 2] is trained on 180 samples. The 
tanh activation is used in the network. The figure below shows 
validation performances of the grey-box and augmented 
hybrid models.

\begin{figure}[!h]
  \centering
  \includegraphics[page=2, width=\textwidth]{tworeac_plots_nonlin.pdf}
\end{figure}

>>>>

In this example, the network just approximates a linear function.
The Figure \ref{fig:validation_linear} 
below shows validation performances of the grey-box 
and augmented hybrid models. The structure 
of the network is restricted to just a matrix and
the augmented model was trained on 240 samples (4 hours).

\begin{figure}[!h]
  \centering
  \includegraphics[page=2, width=\textwidth]{tworeac_plots_lin.pdf}
  \caption{Model validation for the linear plant}
  \label{fig:validation_linear}
\end{figure}

We notice that the augmented model accurately predicts the plant 
behavior. The steady cost profile (Cost = $c_1C_{A0} - c_2C_B$)
is shown in Figure \ref{fig:cost_linear}.

\begin{figure}[!h]
  \centering
  \includegraphics[page=1, width=\textwidth]{tworeac_ssopt_lin.pdf}
  \caption{Steady state cost curve for 
           the linear plant, grey-box, and hybrid model.}
  \label{fig:cost_linear}
\end{figure}

@@

The grey-box model is kept the same. The parameters 
in the model are modified to 
$k_1 = 1 \ \textnormal{m}^3/\textnormal{min}, 
\ k_2 = 0.01 \ \textnormal{m}^3/\textnormal{min},
\ k_3 = 0.05 \ \textnormal{m}^3/\textnormal{min}$, 
and $\tau = 5 \ \textnormal{min}$.
An augmented model with a neural
network architecture [8, 4, 2] is trained on 360 samples (6 hours). 
The tanh activation is used in the network. The figure below shows 
validation performances of the grey-box and augmented 
hybrid models.

\begin{figure}[!h]
  \centering
  \includegraphics[page=2, width=\textwidth]{tworeac_plots_nonlin.pdf}
  \caption{Model validation for the non linear plant}
  \label{fig:validation_nonlinear}
\end{figure}

We notice that the augmented model accurately predicts the plant 
behavior. The steady cost profile (Cost = $c_1C_{A0} - c_2C_B$)
is shown in Figure \ref{fig:cost_nonlinear}. Upon optimization 
using casadi, the optimum cost and control for the plant are: $-19.62 \$$ 
and 1.13 $\textnormal{mol}/\textnormal{m}^3$, and for the hybrid 
grey-box and NN model are: $-19.91 \$$ 
and 1.11 $\textnormal{mol}/\textnormal{m}^3$.

\begin{figure}[!h]
  \centering
  \includegraphics[page=1, width=\textwidth]{tworeac_ssopt_nonlin.pdf}
  \caption{Steady state cost curve for the nonlinear plant, grey-box, and hybrid model.}
  \label{fig:cost_nonlinear}
\end{figure}
